---
title: "Testing the Dimensions with CIFTI Files"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Testing the Dimensions with CIFTI Files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install_dir = tempfile()
dir.create(install_dir)
```

# Load MSC data and test data from cifti package 
Using `download_cifti_data()` and `download.file` to download the test data.

```{r}
library(cifti)
download_cifti_data(outdir = install_dir)

mscfile = file.path(
  install_dir, 
  "sub-MSC01_ses-func01_task-rest_bold_32k_fsLR.dtseries.nii")
if (!file.exists(mscfile)) {
  res = download.file(url = paste0(
    "https://openneuro.org/crn/datasets/ds000224/snapshots/00002/files/", 
    "derivatives:", "surface_pipeline:", "sub-MSC01:",
    "processed_restingstate_timecourses:",  "ses-func01:cifti:",
    "sub-MSC01_ses-func01_task-rest_bold_32k_fsLR.dtseries.nii"), 
    destfile = mscfile)
}
```

```{r}
test_dir = file.path(install_dir, "cifti-2_test_data")

ds <- read_cifti(
  file.path(test_dir,
            "Conte69.MyelinAndCorrThickness.32k_fs_LR.dscalar.nii")
  )
dt <- read_cifti(
  file.path(test_dir,
            "Conte69.MyelinAndCorrThickness.32k_fs_LR.dtseries.nii")
  )
pt <- read_cifti(
  file.path(test_dir,
            "Conte69.MyelinAndCorrThickness.32k_fs_LR.ptseries.nii")
  )
dl <- read_cifti(
  file.path(test_dir, 
            "Conte69.parcellations_VGD11b.32k_fs_LR.dlabel.nii") 
  )
msc <- read_cifti(mscfile, trans_data = FALSE)
msc_trans <- read_cifti(mscfile, trans_data = TRUE)
```


## For reference: MSC 01 (65890 * 818) (using matlab ft_read_cifti), showing first 5 rows & columns
```{r, echo = FALSE}
matfile = system.file("extdata", "msc01_10by10.csv.gz", package = "cifti")
mat = read.csv(matfile, header = FALSE)
msc01_refmat <- as.matrix(mat)
print(msc01_refmat[1:5,1:5])
```
## MSC Sub-01 Session 1 (sub-MSC01_ses-func01_task-rest_bold_32k_fsLR.dtseries.nii)

`read_cifti(fname = , trans_data = FALSE)`
* header dimension shows 65890 * 818
* read in file shows 65890 * 818 by setting trans_data to *FALSE*

```{r}
msc$hdr
dim(msc$data)

msc$data[1:5,1:5]
```

* If transepose is not set to *FALSE* (default is *TRUE*), it will return a 818 * 65890 that is filled correctly, and user just have to `t()` the `cii$data`
```{r}
t(msc_trans$data[1:5,1:5])
```

## Data where dimensions are row x dense loads fine. Updated function loads them the same way as before.
### Conte69.MyelinAndCorrThickness.32k_fs_LR.dscalar.nii

* Dense file "d", vertex level data
* Header shows dimension as rows * dense
```{r}
ds$hdr
attributes(ds$BrainModel[[1]])
attributes(ds$BrainModel[[2]])
dim(ds$data)
head(ds$data)
```

### Conte69.MyelinAndCorrThickness.32k_fs_LR.dtseries.nii

```{r}
dt$hdr
attributes(dt$BrainModel[[1]])
attributes(dt$BrainModel[[2]])
dim(dt$data)
head(dt$data)
```

### Conte69.MyelinAndCorrThickness.32k_fs_LR.ptseries.nii 

* parcel level
```{r}
pt$hdr
dim(pt$data)
head(pt$data)
```


### Conte69.parcellations_VGD11b.32k_fs_LR.dlabel.nii (dense label on vertex level)

* dense label
```{r}
dl$hdr
dim(dl$data)
head(dl$data)
```


